Learning to Synthesize Rules for Rule-based Intrusion Detectors

### 2020-03-05 paper/paper.tex
balancing columns
pending changes on section 4.3.4

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Learning to Synthesize Rules for Network Intrusion Detectors}

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=0.5]{figs/http_header-example.png}
\caption{\CodeIn{http\_header} example.\Mar{Lucas, simplifique esta
    figura (reduza o tamanho da imagem). Mostre apenas os casos onde ha um match, por exemplo,
    com host=www.google.com e connection=keep-alive.}}
\label{fig:http-header-example}
\end{figure}

@@

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

>>>>

%%
%% The "title" command has an optional parameter,
%% allowing the author to define a "short title" to be used in page headers.
\title{Learning to Synthesize Rules for Rule-based Intrusion Detectors}

@@

\begin{figure}[t!]
\centering
\includegraphics[scale=0.5]{figs/http_header-example.png}
\caption{\CodeIn{http\_header} example.}
\label{fig:http-header-example}
\end{figure}

@@

\balance
\bibliographystyle{ACM-Reference-Format}
\bibliography{references}
